---
output: github_document
---

Create your own color palettes and apply them in `ggplot2` in a breeze. All you
have to do is deliver the hex codes from you company or maybe derived from your
favorite paintings? Based on the great work by the [ochRe team](https://github.com/ropenscilabs/ochRe). 

Input is either a named `list` with palettes, or a single palette. (A palette
is a character vector with hex codes of the colors.) Use `viz_pallette` to view 
all the colors in a palette

```{r}
viz_palette(ochre_palettes$lorikeet, "lorikeet colors")
```

From both a list of palettes and a single palette, you can create your own 
`scale_fill` and `scale_color` functions to be used in `ggplot2`. If these are
based on a list of palettes, the functions will have an argument to select which 
of the palettes in the list to use. 

```{r}
# based on a single palette:
my_comp_fill <- get_scale_fill(get_pal(my_company_cols))
my_comp_col  <- get_scale_color(get_pal(my_company_cols))


ggplot(mtcars, aes(mpg, drat, col = as.character(cyl))) +
  geom_point(size = 4) +
  my_comp_col()

ggplot(mtcars, aes(as.character(cyl), fill = as.character(cyl))) +
  geom_bar() +
  my_comp_fill()

# based on a list of palettes:
dutchmasters_fill <- get_scale_fill(get_pal(dutchmasters))
dutchmasters_col  <- get_scale_color(get_pal(dutchmasters))

# scales based on lists default to the first palette
ggplot(mtcars, aes(mpg, drat, col = as.character(cyl))) +
  geom_point(size = 4) +
  dutchmasters_col()

ggplot(mtcars, aes(as.character(cyl), fill = as.character(cyl))) +
  geom_bar() +
  dutchmasters_fill("little_street")
```

The scales search for optimal contrast within the colors provided. The function
`get_hex` creates a function that returns requested hex codes. It is created 
from a named palette. The returned function allows you to query with unquoted
color names.

```{r}
my_company_cols
mc_hex <- get_hex(my_company_cols)
mc_hex(yellow, blue, red)

staalmeesters_hex <- get_hex(dutchmasters$staalmeesters)
ggplot(mtcars, aes(as.character(cyl), fill = as.character(cyl))) +
  geom_bar()  +
  scale_fill_manual(values = staalmeesters_hex(
    red(tablecloth), black(cloak), skin
  ))
```


